---
title: "homework five"
author: "Yi Chen(yc3356)"
date: "February 23, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Challenge Problem I
## Part One

```{r}
#input the data
social_economics <- c(rep('low',4),rep('Median',4),rep('high',4))
Boy_Scout <- c(rep(c(rep('Yes',2),rep('No',2)),3))
deliquency <- c(rep(c('Yes','No'),6))
frequency <- c(10,40,40,160,18,132,18,132,8,192,2,48)

data <- as.data.frame(cbind(social_economics,Boy_Scout,deliquency,frequency))
data
```

First, I want to know how much the social economics status and boy scout would influence the deliquency. i.e. I want the deliquency to be the response variable in the model and the other two to be the predictor variables.
```{r}
social_economics <- factor(c(rep('low',2),rep('Median',2),rep('high',2)))
Boy_Scout <- factor(c(rep(c(rep('Yes',1),rep('No',1)),3)))
deliquency_yes <- c(10,40,18,18,8,2)
deliquency_no <- c(40,160,132,132,192,48)
data_1 <- as.data.frame(cbind(social_economics,deliquency_yes,deliquency_no))
data_1
```

```{r}
new_data <- social_economics <- factor(c(rep('low',1),rep('Median',1),rep('high',1)))
deliquency_yes <- c(50,36,10)
deliquency_no <- c(200,264,240)
data_1 <- as.data.frame(cbind(social_economics,deliquency_yes,deliquency_no))
data_1
```


```{r}
logit1 <- glm(formula = cbind(deliquency_yes,deliquency_no)~factor(Boy_Scout)+factor(social_economics),family = binomial)
summary(logit1)
```

```{r}
predict(logit1,type = 'response')
```

```{r}
residuals(logit1, type="deviance")
```


**Analysis of t test**

As we can see from the table:

First: among two factors(social economic status and boy scout), we have the 95 percent confidence to conclude that: social economics status has signigicant effect on whether the boy will deliquncy. But boy scout do not have significant effect. 

**Analysis of estimation**
Second: for the analysis of the estimated parameters

1. for $b_0=-3.178$(intercept): a boy who has high level social economics status and have not been boy scout before, on average, we have 95% confidence estimate that the odd of this boy is deliquent is $e^{-3.178}=0.04166891$.

2. for $b_1=1.792$(social_economics low): Fixed boy scout(i.e. both have been boy scout before or both not), on average, we have 95% confidence estimate the odds odd of a boy has low level social economics status is deliquent is to be $e^{1.792}=6.001443$ times the odds that  boy who has high level social economics status (a 500% increase roughly)

3. for $b_2=1.186$(social_economics median): Fixed boy scout(i.e. both have been boy scout before or both not), on average, we have 95% confidence estimate the odds odd of a boy has median level social economics status  is deliquent is to be $e^{1.186}=3.273959$ times the odds that boy who has high level social economics status (a 227% increase roughly)

4. for $b_3=-3.956e-16$(Boy_Scout Yes): Fixed social economics status(i.e. both comes from the same social economics status), on average, we have 95% confidence estimate the odds odd of a boy has been boy scout before is deliquent is to be $e^{1.186}=1$ times the odds that boy who has not been boy scout (i.e. there has no significant difference betwenn who attend boy scout or not)

```{r}
confint(logit1)
```

**Analysis of t confidence interval**

Thrid, for the confidence interval:

1. for $b_0$(intercept): a boy who has high level social economics status and have not been boy scout before, on average, we have 95% confidence to conclude that the odd of this boy is deliquent is between $e^{-3.9776309}=0.01872996$ and $e^{-2.4766143}=0.08402724$.

2. for $b_1$(social_economics low): Fixed boy scout(i.e. both have been boy scout before or both not), on average, we have 95% confidence to conclude the odds odd of a boy has low level social economics status is deliquent is to be between $e^{0.4832948}=1.621408$ and $e^{1.9723094}=7.187256$ times the odds that  boy who has high level social economics status

3. for $b_2$(social_economics median): Fixed boy scout(i.e. both have been boy scout before or both not), on average, we have 95% confidence to concludethe odds odd of a boy has median level social economics status  is deliquent is to be between $e^{1.0633292}=2.895996$ and $e^{2.6037768}=13.51468$ times the odds that boy who has high level social economics status

4. for $b_3$(Boy_Scout Yes): Fixed social economics status(i.e. both comes from the same social economics status), on average, we have 95% confidence to conclude the odds odd of a boy has been boy scout before is deliquent is to be between $e^{-0.4971858}=0.60824$ and $e^{0.4897023}=1.63183$ times the odds that boy who has not been boy scout

## Part Two
First, I want to know how much the social economics status and boy scout would influence the deliquency. i.e. I want the deliquency to be the response variable in the model and the other two to be the predictor variables.
```{r}
social_economics <- factor(c(rep('low',2),rep('Median',2),rep('high',2)))
deliquency <- factor(c(rep(c(rep('Yes',1),rep('No',1)),3)))
boy_scout_yes <- c(10,40,18,132,8,192)
boy_scout_no <- c(40,160,18,132,2,48)
data_2 <- as.data.frame(cbind(social_economics,deliquency,boy_scout_yes,boy_scout_no))
data_2
```

```{r}
logit2 <- glm(formula = cbind(boy_scout_yes,boy_scout_no)~factor(social_economics)+factor(deliquency),family = binomial)
summary(logit2)
```

**Analysis of t test**

As we can see from the table:

First: among two factors(social economic status and deliquency), we have the 95 percent confidence to conclude that: social economics status and deliquency has signigicant effect on whether the boy will deliquncy.

**Analysis of estimation**
Second: for the analysis of the estimated parameters

1. for $b_0=1.386$(intercept): a boy who has high level social economics status and have not been deliquent before, on average, we have 95% confidence estimate that the odd of this boy has been boy scout is $e^{1.386}=3.998823$.

2. for $b_1=-2.773$(social_economics low): Fixed deliquency(i.e. both have been deliquent or both not), on average, we have 95% confidence estimate the odds odd of a boy has low level social economics status is deliquent is to be $e^{-2.773}=0.0624743$ times the odds that  boy who has high level social economics status (a 94% decrease roughly)

3. for $b_2=-1.386$(social_economics median): Fixed deliquency(i.e. both have been boy scout before or both not), on average, we have 95% confidence estimate the odds odd of a boy has median level social economics status has been boy scout before is to be $e^{-1.386}=0.2500736$ times the odds that boy who has high level social economics status (a 75% decrease roughly)

4. for $b_3=-9.279e-16$(Boy_Scout Yes): Fixed social economics status(i.e. both comes from the same social economics status), on average, we have 95% confidence estimate the odds odd of a boy who is deliquent has been boy scout before is to be $e^{-9.279e-16}=1$ times the odds that boy who is not deliquent (i.e. there has no significant difference betwenn who attend boy scout or not)

```{r}
confint(logit2)
```

**Analysis of t confidence interval**

Thrid, for the confidence interval:

1. for $b_0$(intercept): a a boy who has high level social economics status and have not been deliquent before, on average, we have 95% confidence to conclude that the odd of this boy has been boy scout before is between $e^{1.0846875}=1.088377$ and $e^{1.7071188}=5.513054$.

2. for $b_1$(social_economics low): Fixed deliquency(i.e. both have been deliquent or both not), on average, we have 95% confidence estimate the odds odd of a boy has low level social economics status is deliquent is to be $e^{-3.2281262}=0.03963169$ and $e^{1.9723094}=0.09665871$ times the odds that  boy who has high level social economics status

3. for $b_2$(social_economics median):  Fixed deliquency(i.e. both have been boy scout before or both not), on average, we have 95% confidence estimate the odds odd of a boy has median level social economics status has been boy scout before is to be $e^{-1.7788290}=0.1688357$ and $e^{-1.0062695}=0.3655802$ times the odds that boy who has high level social economics status

4. for $b_3$(Boy_Scout Yes): Fixed social economics status(i.e. both comes from the same social economics status), on average, we have 95% confidence estimate the odds odd of a boy who is deliquent has been boy scout before is to be between $e^{-0.4971858}=0.60824$ and $e^{0.4897023}=1.63183$ times the odds that boy who is not deliquent


