---
title: "Homework four"
author: "Yi Chen(yc3356)"
date: "February 19, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Homework Four
### problem one
```{r}
setwd("C:/Users/cheny/Desktop/study/second term/Advanced Data Analysis/homework/homework four")
data <- read.csv("mileage.csv",header = TRUE)
```
####(a)
```{r}
fit_1 <- lm(y~factor(x1) + x2,data = data)
summary(fit_1)
```

**analysis**

1. the estimated value of $\beta_0 = 32.0171$. This means that, for premium unleaded gasoline types A, if gasoline additive VST is 0, the average of the gasoline mileage is estimated to be 32.0171.

2. the estimated value of $\beta_1 = 1.5218$. This means that, if fix gasoline additive VST to be the same, for premium unleaded gasoline types B on the average will have 1.5218 higher gasoline mileage than premium unleaded gasoline types A.

3. the estimated value of $\beta_2 = 0.5252$This means that, if fix gasoline additive VST to be the same, for premium unleaded gasoline types C on the average will have 0.5252 higher gasoline mileage than premium unleaded gasoline types A.

4. the estimated value of $\beta_3 = -0.4192$. This means that, if fix the premium unleaded gasoline types to be the same, if we increase 1 unit of gasoline additive VST, on the average the gasoline mileage will decrease 0.4192.

####(b)
```{r}
confint(fit_1,level = 0.95)
```

**analysis**

Based on the data, we are 95% confident  that the "true" $\beta_1$(marginal effect of premium unleaded gasoline types B compared with type A) is between -1.135886 and 4.1795680. 

This also show that:for current significance level, we cannot reject the hyphothesis that $\beta_1=0$. There may have no difference for the marginal effect of premium unleaded gasoline types B compared and type A. Since, this confidence interval include the point 0.

(c)
```{r}
anova(fit_1)
```

**analysis**

As we can see from the anova table, the F-value for factor(x1) (which is related to $\beta_1$ and $\beta_2$) is 0.6989. And the p-value of this F test is 0.5101, which is bigger than $\alpha = 0.05$.

Thus, we can conclude that we fail to reject the hyphothesis that $\beta_1=\beta_2=0$ for current data and significance level. And there may have no significant differenct between different premium unleaded gasoline types' effect on the gasoline mileage.
