---
title: "ADA week One"
author: "Yi Chen(yc3356)"
date: "January 21, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Advanced Data Analysis
### Sign Test for a population **median**

#### Example One
```{r message=FALSE, warning=FALSE}
library(BSDA)

Income = c(7,1110,7.1,5.2,8,12,0,5,2.1,2,46,7.5)
```

```{r}
par(mfrow=c(1,3))
hist(Income)
boxplot(Income)
qqnorm(Income)
qqline(Income,col='red')
```

- As we can see from the plot, the distribution of the data is very has a outlier which is very big.
```{r}
summary(Income)
```

```{r}
t.test(Income,mu=1)
```
- As we can see the intervavl here is [-101,303] which is extremly big and unreliable.Because this data has a very big outlier. Median is a better repesentation for the location of the data

```{r}
SIGN.test(Income,md=1,alternative = 'two.sided')
```
- Here as we can see the intercal is [2.4,11.6] which is very reasonable for the estimation for the sample median


### Example Two
```{r}
age = c(54,42,51,54,49,56,33,58,54,64,49)
sort(age)
```

```{r}
summary(age)
```
```{r}
library(ggplot2)
ggplot()+
        geom_histogram(aes(age,..density..),bins=7)+
        geom_line(aes(age,..density..),stat = 'density')
```
```{r}
boxplot(age)
```

```{r}
qqnorm(age)
qqline(age)
```

- mild deviation from normality in the left tail.

```{r}
t.test(age, mu = 50);
SIGN.test(age,md=50)
```
- similar result and both have good performace

## Wilcoxon Signed Rank Test
### For one case
```{r}
x = c(20,18,23,5,14,8,18,22)
wilcox.test(x,mu=10,conf.int = TRUE,correct = FALSE)
```

### for paired data
```{r}
a = c(0.7,-1.6,-0.2,-1.2,0.1,3.4,3.7,0.8,0.0,2.0)
b = c(1.9,0.8,1.1,0.1,-0.1,4.4,5.5,1.6,4.6,3.0)

d = a - b
sleep = data.frame(a,b,d)
shapiro.test(sleep$d)

wilcox.test(d,mu=0,conf.int = TRUE)
```

